Calibration tests beyond classification

### 2021-03-15 paper/main.tex
Add additional compilation step
Display author names
Add links to experiments and extend abstract as suggested by reviewer

% arara: pdflatex: { shell: yes }
% arara: bibtex
% arara: pdflatex: { shell: yes }
% arara: pdflatex: { shell: yes }
\documentclass{article}

@@

% \iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.

@@

\begin{abstract}
Most supervised machine learning tasks are subject to irreducible prediction
errors. Probabilistic predictive models address this limitation by providing
probability distributions that represent a belief over plausible targets,
rather than point estimates. Such models can be a valuable tool in
decision-making under uncertainty, provided that the model output is
meaningful and interpretable. Calibrated models guarantee that the probabilistic
predictions are neither over- nor under-confident. In the machine learning literature,
different measures and statistical tests have been proposed and studied
for evaluating the calibration of classification models. For
regression problems, however, research has been focused on a weaker
condition of calibration based on predicted quantiles for real-valued targets.
In this paper, we propose the first framework that unifies calibration evaluation and
tests for general probabilistic predictive models. It applies to any such model, including
classification and regression models of arbitrary dimension. Furthermore,
the framework generalizes existing measures and provides a more intuitive
reformulation of a recently proposed framework for calibration in
multi-class classification.
\end{abstract}

@@

Within this framework a KCE for general target spaces is obtained. We want to highlight
that for multi-class classification problems its formulation is more intuitive and
simpler to use than the measure proposed by \citet{Widmann2019} based on matrix-valued
kernels.
To ease the application of the KCE we derive several
estimators of the KCE with subquadratic sample complexity and their asymptotic properties
in tests for calibrated models, which improve on existing estimators and tests in the
two-sample test literature by exploiting the special structure of the calibration
framework. Using the proposed framework, we numerically evaluate the calibration of neural
network models and ensembles of such models.\footnote{The code of the experiments
is available at \url{https://github.com/anonymous/forpeerreview}.}

>>>>

% arara: pdflatex: { shell: yes }
% arara: bibtex
% arara: pdflatex: { shell: yes }
% arara: pdflatex: { shell: yes }
% arara: pdflatex: { shell: yes, synctex: yes }
\documentclass{article}

@@

\iclrfinalcopy % Uncomment for camera-ready version, but NOT for submission.

@@

\begin{abstract}
Most supervised machine learning tasks are subject to irreducible prediction
errors. Probabilistic predictive models address this limitation by providing
probability distributions that represent a belief over plausible targets,
rather than point estimates. Such models can be a valuable tool in
decision-making under uncertainty, provided that the model output is
meaningful and interpretable. Calibrated models guarantee that the probabilistic
predictions are neither over- nor under-confident. In the machine learning literature,
different measures and statistical tests have been proposed and studied
for evaluating the calibration of classification models. For
regression problems, however, research has been focused on a weaker
condition of calibration based on predicted quantiles for real-valued targets.
In this paper, we propose the first framework that unifies calibration evaluation and
tests for general probabilistic predictive models. It applies to any such model, including
classification and regression models of arbitrary dimension. Furthermore,
the framework generalizes existing measures and provides a more intuitive
reformulation of a recently proposed framework for calibration in
multi-class classification. In particular, we reformulate and generalize the
kernel calibration error, its estimators, and hypothesis tests using scalar-valued
kernels, and evaluate the calibration of real-valued regression
problems.\footnote{The source code of the experiments is available at
  \url{https://github.com/devmotion/Calibration_ICLR2021}.}
\end{abstract}

@@

Within this framework a KCE for general target spaces is obtained. We want to highlight
that for multi-class classification problems its formulation is more intuitive and
simpler to use than the measure proposed by \citet{Widmann2019} based on matrix-valued
kernels.
To ease the application of the KCE we derive several
estimators of the KCE with subquadratic sample complexity and their asymptotic properties
in tests for calibrated models, which improve on existing estimators and tests in the
two-sample test literature by exploiting the special structure of the calibration
framework. Using the proposed framework, we numerically evaluate the calibration of neural
network models and ensembles of such models.
